Problem of Step 4 (debias) of fGFPCA on NHANES data

### 2024-02-20 Docs/NhanesApplExample.Rmd
appendix figure

```{r}
# PC functions after re-evaluation
bind_rows(
  data.frame(sind=1:J, est_phi*sqrt(n_bin), type = "re-evaluated"),
  data.frame(df_phi, type = "True")
) %>%
  pivot_longer(2:5) %>%
  ggplot()+
  geom_line(aes(x=sind, y=value, col=type))+
  facet_wrap(~name)
```

>>>>

```{r}
theme_set(theme_minimal())
cols <- c(brewer.pal(4, "Set2"), "#000000") # define a color palette 
names(cols) <- c("0.2", "0.4", "0.6", "0.8", "True")

# PC functions after re-evaluation
bind_rows(
  data.frame(sind=1:J, est_phi*sqrt(n_bin), type = "Simulation"),
  data.frame(df_phi, type = "Generation")
) %>%
  rename("PC1" = phi1, "PC2" = phi2, "PC3" = phi3, "PC4" = phi4) %>%
  pivot_longer(2:5) %>%
  ggplot()+
  geom_line(aes(x=sind, y=value, col=type), linewidth=1)+
  facet_wrap(~name)+
  scale_color_brewer(palette = "Set2")+
   scale_x_continuous(breaks = seq(0, 1440, by = 360),
                     labels = c("0am", "6am", "12pm", "6pm", "12am"))+
  labs(x = "Time", y="", color = "")
```
